---
title: "Week 8 Class"
author: "Samantha-Jo Caetano"
date: "March 10 or 11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


First let's load in the Starbucks data. 

```{r, include=FALSE}
starbucks<-read_csv("starbucks.csv")
```


## For all Pastries

Now, let's look at the mean, standard deviation and sample size of the calorie variable.

```{r}
starbucks %>%   
  summarise(
  mean_cal = mean(calories),
  sd_cal = sd(calories),
  n_cal = n())

```


Or in base R:

```{r}
xbar_cal <- mean(starbucks$calories)
s_cal <- sd(starbucks$calories)
n_cal <- length(starbucks$calories)
```

The 95% CI for mean calories is `r xbar_cal - qnorm(0.975)*s_cal/n_cal` to `r xbar_cal + qnorm(0.975)*s_cal/n_cal`. Here we are assuming that $n=77$ is relatively large.


## For Petite Pastries only

```{r}
starbucks_petite <- starbucks %>% filter(type == "petite")
```

```{r}
xbar_cal_p <- mean(starbucks_petite$calories)
s_cal_p <- sd(starbucks_petite$calories)
n_cal_p <- length(starbucks_petite$calories)
```


The 95% CI for mean calories in petite pastries is `r xbar_cal_p - qt(0.975, n_cal_p-1)*s_cal_p/n_cal_p` to `r xbar_cal_p + qt(0.975, n_cal_p-1)*s_cal_p/n_cal_p`. Here we are assuming that $n=$ `r n_cal_p-1` is relatively small.
